Model to study co-evolution of trade an culture

### 2015-03-31 article.tex

\simon{What do you think about puting  the bentley et al resutlts cf table~\ref{tab:Bmualpha} below}

\begin{table}
	\centering
	\begin{tabular}{l|cc}
N=250\\\hline
$\mu$&$\alpha$&(SD)\\\hline
0.004&1.50&(0.02) \\
0.008&1.52&(0.02)\\
0.016&1.55&(0.03)\\
0.032&1.59&(0.06)\\
0.064&1.78&(0.08)\\
0.128&1.99&(0.04)\\
	\end{tabular}
	\begin{tabular}{l|cc}
N=500\\\hline
$\mu$&$\alpha$&(SD)\\\hline
0.004&1.53&(0.03)\\
0.008&1.57&(0.01)\\
0.016&1.61&(0.04)\\
0.032&1.70&(0.05)\\
0.064&1.81&(0.10)\\
0.128&1.98&(0.02)\\
	\end{tabular}
	\caption{Mean \& SD of $\alpha$ parameter }
	\label{tab:Bmualpha}
\end{table}

>>>>

\simon{What do you think about puting  the bentley et al resutlts cf table~\ref{tab:Bmualpha} below?\\ 
By the way, doing t.test on the different value of alpha I have gives me statistically differences between 250 and 500 agents ONLY for $\mu=.064$  }
